---
title: "Exercise 8.1"
author: "Groupe 3"
date: "6/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

8.1. Recreate the simulated data from Exercise 7.2:
```{r}
library(mlbench)
set.seed(200)
simulated <- mlbench.friedman1(200, sd = 1)
simulated <- cbind(simulated$x, simulated$y)
simulated <- as.data.frame(simulated)
colnames(simulated)[ncol(simulated)] <- "y"
```


(a) Fit a random forest model to all of the predictors, then estimate the
variable importance scores:
```{r}
library(randomForest)
library(caret)
model1 <- randomForest(y ~ ., data = simulated,
importance = TRUE,
ntree = 1000)
rfImp1 <- varImp(model1, scale = FALSE)
```

```{r}
rfImp1 
```


Did the random forest model significantly use the uninformative predic-
tors ( V6 – V10 )?


(b) Now add an additional predictor that is highly correlated with one of the
informative predictors. For example:
```{r}
simulated$duplicate1 <- simulated$V1 + rnorm(200) * .1
cor(simulated$duplicate1, simulated$V1)
```

Fit another random forest model to these data. Did the importance score
for V1 change? What happens when you add another predictor that is
also highly correlated with V1 ?


(c) Use the cforest function in the party package to fit a random forest model
using conditional inference trees. The party package function varimp can
calculate predictor importance. The conditional argument of that func-
tion toggles between the traditional importance measure and the modified
version described in Strobl et al. (2007). Do these importances show the
same pattern as the traditional random forest model?


(d) Repeat this process with different tree models, such as boosted trees and
Cubist. Does the same pattern occur?8.8 Computing
219
MolWeight
HydrophilicFactor
NumAromaticBonds
NumCarbon
SurfaceArea1
NumMultBonds
NumAtoms
NumHalogen
FP172
SurfaceArea2
NumNonHAtoms
NumHydrogen
NumBonds
NumRotBonds
NumNonHBonds
FP075
NumRings
FP015
FP072
FP074
FP107
FP070
FP065
FP044
FP104
NumCarbon
MolWeight
SurfaceArea2
SurfaceArea1
HydrophilicFactor
NumNonHAtoms
NumBonds
NumHydrogen
FP059
FP135
FP092
FP198
FP077
NumMultBonds
NumRotBonds
NumAtoms
NumOxygen
NumHalogen
NumNonHBonds
FP176
NumChlorine
FP137
FP205
FP141
NumAromaticBonds
0
200 400 600
Importance
0
500
1000
Importance
Fig. 8.24: A comparison of variable importance magnitudes for differing values
of the bagging fraction and shrinkage parameters. Both tuning parameters
are set to 0.1 in the left figure. Both are set to 0.9 in the right figure